Democratizing Secure Two-Party Computation

### 2017-10-22 OaklandSubmission/ld.tex
text completing s3 except the security theorem

In this section we prove the correctness and security of our compiler.
%
We first formalize the source and target languages. Our source runtime
semantics is a model of the ideal, trusted third-party semantics, and
generates observations corresponding to the values revealed to the
parties.
%
The target language semantics (a model of the C++ code generated by
our compiler implementation) ``computes away'' the public parts of the
compiled program, generating a secure computation circuit.
%
Finally, we formalize the circuit semantics that computes the
generated circuit, and like the source semantics, emits observations.

@@

The target semantics models the semantics of the code output by
our compiler (C++ code in our implementation). It computes over the
public parts of the program, emitting a circuit that can later be
evaluated using a cryptographic MPC protocol. Crucially, this phase of
the semantics does not have access to the secrets.

@@

Figure~\ref{fig:tgtsem} shows the judgments for the target
semantics. We first focus on the expression evaluation judgment
$\widetilde{\rho} \vdash \widetilde{e} \Downarrow
\widetilde{v}$. Rules ({\sc{S-PAdd}}) and ({\sc{S-SAdd}}) illustrate
the significance of the operator labels. In particular, the rule
({\sc{S-PAdd}}) evaluates a public addition $\widetilde{e_{1}}
+_{\mathcal{P}} \widetilde{e_{2}}$ to $n_{1} + n_{2}$, similar to the
source language. In contrast, the rule
({\sc{S-SAdd}}) evaluates a secret addition $\widetilde{e_{1}}
+_{\mathcal{A}} \widetilde{e_{2}}$, using an arithmetic add
gate, to $\kw{add}\:\kappa_{1}\:\kappa_{2}$. Since our compiler
compiles secret add operations to arithmetic gates, the target
expressions from our compiler never have $\widetilde{e_{1}}
+_{\mathcal{B}} \widetilde{e_{2}}$ (we present the compilation rules
later in the section). Rules ({\sc{S-PCond}}) and ({\sc{S-SCond}})
are along the similar lines. Rule ({\sc{S-PCond}}) evaluates a public
conditional to the values from one of the branches, while the rule
({\sc{S-SCond}}) evaluates to a \kw{mux} gate that takes input
circuits from the conditional ($\kappa_{1}$) and both the branches
($\kappa_{2}$ and $\kappa_{3}$). Rules {\sc{S-Coerce}} and
{\sc{S-Inp}} evaluate to the coerce and input gates respectively.

@@

\subsubsection*{Compilation judgments}

\begin{theorem}[Correctness of the compiler]

@@

     \inferrule*[lab={\footnotesize{T-For}}]
               {
                 \Gamma' = \Gamma, x::\kw{uint}^{\mathcal{P}}\\\\
                 \Gamma' \vdash \loops{x}{n_{2}}{s} \leadsto \loops{x}{n_{2}}{\widetilde{s}} \mid \Gamma'
               }
               {
                 \Gamma \vdash \for{x}{n_{1}}{n_{2}}{s} \leadsto \for{x}{n_{1}}{n_{2}}{\widetilde{s}} \mid \Gamma
               }

@@

  \end{array}
  \]
\label{fig:compile}
\caption{Compilation judgments (selected rules)}
\end{figure}

>>>>

In this section we prove the correctness and security of our compiler.
%
We first formalize the source and target languages. Our source runtime
semantics is a model of the ideal, trusted third-party semantics, and
generates observations corresponding to the values revealed to the
parties.
%
The target language semantics (a model of the C++ code generated by
our compiler implementation) ``computes away'' the public parts and
arrays from the compiled program, generating a secure computation
circuit.
%
Finally, we formalize the circuit semantics that computes the
generated circuit, and like the source semantics, emits observations.

@@

The target semantics models the semantics of the code output by
our compiler (C++ code in our implementation). It computes over the
public parts of the program, emitting a circuit that can later be
evaluated using a cryptographic MPC protocol. The semantics also
flattens the circuit so that the circuits are unaware of the array
structure. Crucially, this phase of the semantics does not have access
to the secrets.

@@

Figure~\ref{fig:tgtsem} shows the judgments for the target
semantics. We first focus on the expression evaluation judgment
$\widetilde{\rho} \vdash \widetilde{e} \Downarrow
\widetilde{v}$. Rules ({\sc{S-PAdd}}) and ({\sc{S-SAdd}}) illustrate
the significance of the operator labels. In particular, the rule
({\sc{S-PAdd}}) evaluates a public addition $\widetilde{e_{1}}
+_{\mathcal{P}} \widetilde{e_{2}}$ to $n_{1} + n_{2}$, similar to the
source language. In contrast, the rule
({\sc{S-SAdd}}) evaluates a secret addition $\widetilde{e_{1}}
+_{\mathcal{A}} \widetilde{e_{2}}$, using an arithmetic add
gate, to $\kw{add}\:\kappa_{1}\:\kappa_{2}$. Since our compiler
compiles secret add operations to arithmetic gates, the target
expressions from our compiler never have $\widetilde{e_{1}}
+_{\mathcal{B}} \widetilde{e_{2}}$ (we present the compilation rules
later in the section). Rules ({\sc{S-PCond}}) and ({\sc{S-SCond}})
are along the similar lines. Rule ({\sc{S-PCond}}) evaluates a public
conditional to the values from one of the branches, while the rule
({\sc{S-SCond}}) evaluates to a \kw{mux} gate that takes input
circuits from the conditional ($\kappa_{1}$) and both the branches
($\kappa_{2}$ and $\kappa_{3}$). Rules ({\sc{S-Coerce}}) and
({\sc{S-Inp}}) evaluate to the coerce and input gates respectively.

@@

@@

     \inferrule*[lab={\footnotesize{T-For}}]
               {
                 \Gamma' = \Gamma, x:\kw{uint}^{\mathcal{P}}\\\\
                 \Gamma' \vdash \loops{x}{n_{2}}{s} \leadsto \loops{x}{n_{2}}{\widetilde{s}} \mid \Gamma'
               }
               {
                 \Gamma \vdash \for{x}{n_{1}}{n_{2}}{s} \leadsto \for{x}{n_{1}}{n_{2}}{\widetilde{s}} \mid \Gamma
               }

@@

  \end{array}
  \]
\caption{Compilation judgments (selected rules)}
\label{fig:compile}
\end{figure}

\subsubsection*{Compilation judgments} We now come to the compilation
rules shown in Figure~\ref{fig:compile}. We present the rules in a
declarative style, where the rules are also non-syntax
directed, and the labels $\ell$ are also chosen
non-deterministically.

Judgment $\Gamma \vdash e : \tau \leadsto \widetilde{e}$, where
$\Gamma$ maps variables $x$ to types $\tau$, says that
under $\Gamma$, $e$ compiles to $\widetilde{e}$ with type $\tau$.

The rule ({\sc{T-Cons}}) assigns the label $\mathcal{P}$ to the
constants, as the constants are always public. Rule ({\sc{T-Add}})
compiles an addition to either public addition ($+_{\mathcal{P}}$) or
secret addition using an arithmetic circuit ($+_{\mathcal{A}}$). As
our compiler is cryptographic cost aware, it never compiles the
addition to boolean addition $+_{\mathcal{B}}$. In a similar manner,
rule ({\sc{T-Gt}}) compiles $e_{1} > e_{2}$ to either public comparison
or secret comparison using boolean circuits. The rule for conditional
({\sc{T-Cond}}) has two cases: when the conditional expression $e$ is of
type $\kw{bool}^{\mathcal{P}}$, both the branches have a base type
$\sigma^{\ell'}$, for an arbitrary $\ell'$, and the conditional is
compiled to public conditional, whereas when the conditional
expression has type $\kw{bool}^{\mathcal{B}}$, $\ell'$ is also
$\mathcal{B}$, and the conditional is compiled to a secret conditional
using a boolean circuit. Note that we restrict the type of the branches
to be of base type. Rule ({\sc{T-Read}}) types an array read. It checks
that the array index $e$ is public, and uses a static bounds checking
judgment $\Gamma \models e < n$ to prove that the array index is in
bounds. Section~\ref{sec:impl} discusses our implementation of bounds
checking. Rule ({\sc{T-Inp}}) picks a label $m$ for the input. Finally,
rule ({\sc{T-Sub}}) is the subsumtion rule that coerces an expression of
type $\sigma^{\ell}$ to an expression of type $\sigma^{m}$ using the
coerce expression. Importantly, secrets cannot be coerced to public
values.

Judgment $\Gamma \vdash s : \tau \leadsto \widetilde{s} \mid \Gamma'$
compiles a statement $s$ resulting in the statement $\widetilde{s}$
and type environment $\Gamma'$. Rule ({\sc{T-Decl}}) picks a label
$\ell$, and adds the binding for $x$ to the environment. Rule
({\sc{T-For}}) adds the loop counter $x$ to $\Gamma$ at type
$\kw{uint}^{\mathcal{P}}$, and delegates type checking to the
\kw{while} form. The rule ({\sc{T-Write}}), similar to ({\sc{T-Read}}),
checks that the index is public, and is in bounds. Rule ({\sc{T-Out}})
types the expression $e$ at some secret label $m$. Rule ({\sc{T-If}})
checks that the conditional expression is public, and rule
({\sc{T-Seq}}) sequences the type environments. Finally, the typing
rule for the (internal) \kw{while} form ensures that $x$ is mapped in
$\Gamma$ at type $\kw{uint}^{\mathcal{P}}$, and that $x \notin
\mathsf{modifies}(s)$--this helps us prove the termination.

\subsubsection*{Correctness theorem} We first define a judgment for
translation of type environments, $\Gamma \vdash \rho \leadsto
\widetilde{\rho}; \widehat{\rho_{1}}, \widehat{\rho_{2}}$. The
judgment is defined inductively on $\Gamma$, and establishes that the
the static environment $\Gamma$ is consistent with the runtime
environments $\rho$, $\widetilde{\rho}$, and $\widehat{\rho_{1}}$ and
$\widehat{\rho_{2}}$. As an example, if $x:\kw{uint}^{\mathcal{P}} \in
\Gamma$, the judgment checks that $\rho(x) = \widetilde{\rho}(x) =
n$. We elide the judgment, but it is defined in the supplementary
material.

With this judgment in hand, the correctness theorem is as follows:

\begin{theorem}[Correctness]
  $\forall\:\Gamma, s, \widetilde{s}, \Gamma', \rho, \widetilde{\rho}, \widehat{\rho_{1}}, \widehat{\rho_{2}}$, if:

  \begin{enumerate}
  \item $\Gamma \vdash s \leadsto \widehat{s} \mid \Gamma'$
  \item $\Gamma \vdash \rho \leadsto \widetilde{\rho}; \widehat{\rho_{1}}, \widehat{\rho_{2}}$
  \end{enumerate}

  then $\exists \rho', O_{1}, \widetilde{\rho'}, \chi, \widehat{\rho_{1}'}, \widehat{\rho_{1}'}, O_{2}$, s.t.

  \begin{enumerate}
  \item $\rho \vdash s \Downarrow \rho'; O_{1}$
  \item $\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho'}; \chi$
  \item $\widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \chi \Downarrow \widehat{\rho_{1}'}, \widehat{\rho_{2}'}; O_{2}$
  \item $\Gamma' \vdash \rho' \leadsto \widetilde{\rho'}; \widehat{\rho_{1}'}, \widehat{\rho_{2}'}$
  \item $O_{1} = O_{2}$
  \end{enumerate}

The theorem states that if a source statement $s$ is well-typed, and
compiled to $\widetilde{s}$, then $s$ terminates in the source
semantics with observations $O_{1}$, $\widetilde{s}$ terminates in the
target semantics with circuit $\chi$, and $\chi$ terminates in the
circuit semantics with observations $O_{2}$, where $O_{1} = O_{2}$
Furthermore, the final environments are also in the compilation
relation.

\subsubsection*{Security theorem}
